\propertitle

### 2019-12-05 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-05T11:17:52+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Before applying the formula above to two concrete data sets we want to add
two remarks about the maximum-entropy method that are seldom made in the
neuroscientific literature. They are important for the interpretation of
the results and are further discussed in \sect~\ref{sec:assumptions}.
First, the maximum-entropy
method % (based on the \emph{Shannon} relative
% entropy, as opposed to other entropy functions such as Burg's
% \citeyear{burg1975})
rests on some implicit assumptions about the probabilities for the long-run
frequency distribution of activities, besides the assumptions just
mentioned at the end of the previous paragraph. So the often-heard
statement that it gives \enquote{the maximally unbiased (or non-committal)
  distribution} must be taken with a grain of salt. \citep[\mynote{move to
  sect}]{jaynes1986d_r1996,portamana2009,portamana2017}. Second, a
maximum-entropy distribution like $\px(\yA \| M, N)$ is the zeroth-order
approximation (in the sense of Laplace's approximation
\citep[\chap~4]{debruijn1958_r1961}{tierneyetal1986,strawderman2000}) of
four distinct distributions for the larger population, which differ
numerically from one another in higher-order approximations:
\begin{enumerate}[label=(\roman*)]
\item the most probable \emph{frequency} distribution for the total
  activity across the \emph{recorded} bins, %$\yFF(\yA)$,
\item the \emph{belief} distribution for the value of the total
  activity at any time bin among the \emph{recorded} ones,
  %$\yp(\yA_{t} \| \yH)$ with $1\le t \le T$,
\item the most probable \emph{frequency} distribution for the total
  activity in a very long run of \emph{new} time bins, %$\ynuu(\yA)$,
\item the \emph{belief} distribution for the value of the total
  activity at a \emph{new} time bin.
  % $\yp(\yA_{t} \| \yH)$ with $t<1$ or $t>T$
\end{enumerate}
In the present case the validity of the maximum-entropy approximation
decreases as the ratio $nN/T$ increases (see \sect~\ref{sec:assumptions}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{acknowledgements}
  This work is financially supported by the Kavli Foundation and the Centre
  of Excellence scheme of the  Research Council of Norway (Yasser Roudi group).\\
  PGLPM thanks Mari, Miri, \amp\ Emma for continuous encouragement and
  affection; Buster Keaton and Saitama for filling life with awe and
  inspiration; the developers and maintainers of \LaTeX, Emacs, AUC\TeX,
  Open Science Framework, Python, Inkscape, Sci-Hub for making a free and
  unfiltered scientific exchange possible.
%\rotatebox{15}{P}\rotatebox{5}{I}\rotatebox{-10}{P}\rotatebox{10}{\reflectbox{P}}\rotatebox{-5}{O}.
%\sourceatright{\autanet}
\end{acknowledgements}

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-05T11:25:20+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Before applying the formula above to two concrete data sets we want to add
two remarks about the maximum-entropy method that are seldom made in the
neuroscientific literature. They are important for the interpretation of
the results and are further discussed in \sect~\ref{sec:assumptions}.
First, the maximum-entropy
method % (based on the \emph{Shannon} relative
% entropy, as opposed to other entropy functions such as Burg's
% \citeyear{burg1975})
rests on some implicit assumptions about the probabilities for the long-run
frequency distribution of activities, besides the assumptions just
mentioned at the end of the previous paragraph. So the often-heard
statement that it gives \enquote{the maximally unbiased (or non-committal)
  distribution} must be taken with a grain of salt.
\citep{jaynes1986d_r1996,portamana2009,portamana2017}. Second, a
maximum-entropy distribution like $\px(\yA \| M, N)$ is the zeroth-order
approximation (in the sense of Laplace's approximation
\citep[\chap~4]{debruijn1958_r1961}{tierneyetal1986,strawderman2000}) of
four distinct distributions for the larger population, which differ
numerically from one another in higher-order approximations:
\begin{enumerate}[label=(\roman*)]
\item the most probable \emph{frequency} distribution for the total
  activity across the \emph{recorded} bins, %$\yFF(\yA)$,
\item the \emph{belief} distribution for the value of the total
  activity at any time bin among the \emph{recorded} ones,
  %$\yp(\yA_{t} \| \yH)$ with $1\le t \le T$,
\item the most probable \emph{frequency} distribution for the total
  activity in a very long run of \emph{new} time bins, %$\ynuu(\yA)$,
\item the \emph{belief} distribution for the value of the total
  activity at a \emph{new} time bin.
  % $\yp(\yA_{t} \| \yH)$ with $t<1$ or $t>T$
\end{enumerate}
In the present case the validity of the maximum-entropy approximation
decreases as the ratio $nN/T$ increases (see \sect~\ref{sec:assumptions}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{acknowledgements}
  This work is financially supported by the Kavli Foundation and the Centre
  of Excellence scheme of the  Research Council of Norway (Yasser Roudi group).\\
  PGLPM thanks the staff of the NTNU library for their always prompt
  support; Mari, Miri, \amp\ Emma for continuous encouragement and
  affection; Buster Keaton and Saitama for filling life with awe and
  inspiration; the developers and maintainers of \LaTeX, Emacs, AUC\TeX,
  Open Science Framework, Python, Inkscape, Sci-Hub for making a free and
  unfiltered scientific exchange possible.
%\rotatebox{15}{P}\rotatebox{5}{I}\rotatebox{-10}{P}\rotatebox{10}{\reflectbox{P}}\rotatebox{-5}{O}.
%\sourceatright{\autanet}
\end{acknowledgements}
